Scalar and Representative Observables, and Their Associated Statistical Model, for Polarimetric SAR Data

### 2014-07-28 paper_dev/article_pp.tex
auto

Taking the log-transformation of the above equation, and denoting $C_{vx} = Z_x / L_x$, $C_{vy} = Z_y / L_y$ and $C_{vxy} = (Z_x + Z_y)/(L_x + L_y)$ then:
{\small
\begin{align}
  Q &= \frac{|C_{vx}|^{L_x} \cdot |C_{vy}|^{L_y} }{|C_{vxy}|^{L_x + L_y}} \label{eqn:ori_likelyhood_stats} \\
  \ln Q &= L_x \ln |C_{vx}| + L_y \ln |C_{vy}| - (L_x + L_y) \ln |C_{vxy}| \label{eqn:log_likelyhood_stats}
\end{align}
}

@@

As for the first matter, in view of the models given in Eqn \ref{eqn:determinant_distribution},
  the likelihood test statistics presented in \cite{Conradsen_2003_TGRS_4} and rewritten in Eqns \ref{eqn:ori_likelyhood_stats} \& \ref{eqn:log_likelyhood_stats}
can be expressed as:
\begin{align*}
  \ln{Q} &\sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
  Q &\sim e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}   
\end{align*}
where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
This, in essence, derives an exact statistical distribution for the likelihood test statistics (as opposed to an asymptotic distribution \cite{{Conradsen_2003_TGRS_4}}).

>>>>

Taking the log-transformation of the above equation, and denoting $C_{vx} = Z_x / L_x$, $C_{vy} = Z_y / L_y$ and $C_{vxy} = (Z_x + Z_y)/(L_x + L_y)$ then:
{\small
\begin{align}
  Q &= \frac{|C_{vx}|^{L_x} \cdot |C_{vy}|^{L_y} }{|C_{vxy}|^{L_x + L_y}} \label{eqn:ori_likelyhood_stats} % \\
  % \ln Q &= L_x \ln |C_{vx}| + L_y \ln |C_{vy}| - (L_x + L_y) \ln |C_{vxy}| \label{eqn:log_likelyhood_stats}
%  Q &= \frac{|C_{vx}|^{L_x} \cdot |C_{vy}|^{L_y} }{|C_{vxy}|^{L_x + L_y}} \label{eqn:ori_likelyhood_stats} \\
%  \ln Q &= L_x \ln |C_{vx}| + L_y \ln |C_{vy}| - (L_x + L_y) \ln |C_{vxy}| \label{eqn:log_likelyhood_stats}
\end{align}
}

@@

As for the first matter, in view of the models given in Eqn \ref{eqn:determinant_distribution},
  the likelihood test statistics presented in \cite{Conradsen_2003_TGRS_4} and rewritten in Eqns \ref{eqn:ori_likelyhood_stats} \& \ref{eqn:log_likelyhood_stats}
can be expressed as:
\begin{align*}
%  \ln{Q} &\sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
  Q &\sim e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}   
\end{align*}
%where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
This, in essence, derives an exact statistical distribution for the likelihood test statistics (as opposed to an asymptotic distribution \cite{{Conradsen_2003_TGRS_4}}).
